---
title: "Final Project. Part 2: Basic Inferential Data Analysis Instructions"
author: "Kadyrbek"
date: "11/18/2019"
output:
  pdf_document: default
  html_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Synopsis

In this project we are going to analyze ToothGrowth data from datasets package. We will compare the length of odontoblasts by supplement types and doses amounts.

#1. Load the ToothGrowth data and perform some basic exploratory data analyses

Here is some exploratory data analyses of ToothGrowth data
```{r}
library(datasets)
head(ToothGrowth)
str(ToothGrowth)
```
#2. Provide a basic summary of the data.
```{r}
summary(ToothGrowth)
```
From the table above we can see that there are 60 observations with two supplement types 30 observation each. There are 3 types of dose amounts 0.5, 1 and 2.

```{r}
boxplot(ToothGrowth$len~ToothGrowth$supp)
```

#3. Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.

Here are confidence intervals for supplement types.
```{r}
oj<-ToothGrowth[ToothGrowth$supp=="OJ",]
vc<-ToothGrowth[ToothGrowth$supp=="VC",]
ojt<-t.test(oj$len, alternative = "two.sided",conf.level = .8)$conf
vct<-t.test(vc$len, alternative = "two.sided",conf.level = .8)$conf
list("OJ interval"=ojt,"VC interval"=vct)
t.test(oj$len,vc$len)
```

Here are confidence intervals for different dose amounts. 
```{r}
half<-ToothGrowth[ToothGrowth$dose==0.5,]
one<-ToothGrowth[ToothGrowth$dose==1,]
two<-ToothGrowth[ToothGrowth$dose==2,]
ht<-t.test(half$len, alternative = "two.sided")$conf
ot<-t.test(one$len, alternative = "two.sided")$conf
tt<-t.test(two$len, alternative = "two.sided")$conf
list("Half dose interval"=ht,"One dose interval"=ot,"Two dose interval"=tt)
```

#4. State your conclusions and the assumptions needed for your conclusions.

The p-value of T test for different supplement type is equal to 0.06 and slightly above the 0.05. This tells us that it is not significant or it slightly significant. 
Confidence interval of OJ is higher and narrower than VC  with confidence level of 80%. If we use confidence level of 95% as we do it usual then their intervals intersept, which says there is no 95% confidence in the observations.

However, in comparing the length for different dose amounts, it is stright forward. 0.5 dose length values are less than 1 dose, and 1 dose values are less than 2 dose values with confidence level of 95%. 
